---
title: "NPS park climate futures"
author: "Climate Change Response Program"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

```{r setup, warning=FALSE, include = FALSE}

knitr::opts_chunk$set(
  echo = FALSE, 
  collapse = TRUE,
  warning = TRUE, # set to FALSE when done
  message = TRUE # set to FALSE when done
)

library(here); library(plyr); # Use here::here when package lubridate is used
library(plotrix); library(zoo); library(ggplot2); library(grid); library(cowplot); library(reshape2); library(raster); library(ncdf4); library(reshape2); library(WriteXLS); library(data.table); library(RColorBrewer); library(ggrepel); library(lubridate); library(dplyr); library(forcats); library(openxlsx); library("WaterBalance"); library(sf); library(raster); library(rgdal); library(R.utils); library(tmap); library(tmaptools); library(ggspatial); library(basemaps)
library(gridExtra); library(SPEI); library(tidyr); library(tibble); library(sp); library(skimr);  library(stringr); library(ggpubr); library(lemon); library(ggfortify); library(extRemes); library(sp);library(terra);library(rasterVis); library(sf)


```


# For loop that reads names from csv file for park

```{r user-inputs-1, warning=FALSE, include = FALSE}

rm(list = ls())
#### Use existing RCF file at OutDir

```


```

```{r WarmWet/HotDry, message=FALSE, warning=FALSE, include = FALSE}
# Specify Climate Futures

OutDir <- "C:/Users/arunyon/OneDrive - DOI/Documents/Projects/SFAN-P4CC-workshop/PORE/PORE/"

DataDir = paste0(OutDir,'input-data/') # for .csv's

DataFile <- list.files(path = DataDir, pattern = 'Final_Environment.RData', full.names = TRUE) 

# Environment needs to be added if not parsing MACA data
load(DataFile)
OutDir <- "C:/Users/arunyon/OneDrive - DOI/Documents/Projects/SFAN-P4CC-workshop/PORE/PORE/"
DataDir = paste0(OutDir,'input-data/') # for .csv's

FutureSubset <- c("Warm Wet", "Hot Dry")
CFs = FutureSubset 
custom_GCMs = c("CNRM-CM5.rcp45", "MIROC-ESM-CHEM.rcp85") # In order as FutureSubset

CF_abbreviation <- "Custom-CFs"

colors2<- colors5[c(1,4)] # Select pair of climate futures - WarmWet/HotDry

colors3<-c("white",colors2)
col<- c("darkgray",colors2)  # WarmWet/HotDry
#col<- c("darkgray","#F3D3CB","#12045C")  # HotWet/WarmDry

## Adjust CFs
WB_GCMs <- data.frame(GCM = custom_GCMs, CF = CFs)

#Change selected CFs in Future_Means df
Future_Means$select <- NA
Future_Means$select[Future_Means$GCM == WB_GCMs$GCM[1]] = WB_GCMs$CF[1]
Future_Means$select[Future_Means$GCM == WB_GCMs$GCM[2]] = WB_GCMs$CF[2]

CFDir = paste0(OutDir,"Custom-CFs/") # for .csv's
if(dir.exists(CFDir) == FALSE){
  dir.create(CFDir)
}

TableDir = paste0(CFDir,"tables/") # for .csv's
if(dir.exists(TableDir) == FALSE){
  dir.create(TableDir)
}

FigDir = paste0(CFDir,"figures/") # for .csv's
if(dir.exists(FigDir) == FALSE){
  dir.create(FigDir)
}

# Run scripts
source(here::here("scripts", "Threshold_Bar_Charts.R")) # Requires "PARK_lat_long_Final_Environment.RData". Outputs plots and Excel Workbook 

source(here::here("scripts","Daily_WB_Model.R"))

source(here::here("scripts", "Drought_characteristics.R"))

source(here::here("scripts", "Return_Events.R"))

source(here::here("scripts", "Summary plots.R"))

source(here::here("scripts", "Report_plots.R"))

```

```{r WarmDry/HotWet, message=FALSE, warning=FALSE, include = FALSE}
# Specify Climate Futures
DataFile <- list.files(path = DataDir, pattern = 'Final_Environment.RData', full.names = TRUE) # Environment needs to be added if not parsing MACA data
load(DataFile)

FutureSubset <- CFs_all[c(4,2)]; CFs = FutureSubset  # Pick pair of climate futures.
CF_abbreviation <- "WD-HW"

# WB_GCMs <- subset(WB_GCMs, CF %in% CFs)

# colors2<- c("#9A9EE5","#E10720")  # Select pair of climate futures - WarmWet/HotDry
colors2<- colors5[c(3,2)] # Select pair of climate futures - HotWet/WarmDry

colors3<-c("white",colors2)
# col<- c("darkgray","#9A9EE5","#E10720")  # WarmWet/HotDry
col<- c("darkgray", colors2)  # HotWet/WarmDry

CFDir = paste0(OutDir,"WarmDry_HotWet/") # for .csv's
if(dir.exists(CFDir) == FALSE){
  dir.create(CFDir)
}

TableDir = paste0(CFDir,"tables/") # for .csv's
if(dir.exists(TableDir) == FALSE){
  dir.create(TableDir)
}

FigDir = paste0(CFDir,"figures/") # for .csv's
if(dir.exists(FigDir) == FALSE){
  dir.create(FigDir)
}

if (exists("FutureSubset") == FALSE) stop("Please specify Climate Futures") # At the top of the script, please enter a combination of futures, e.g. Warm Wet/Hot Dry

source(here::here("scripts", "Threshold_Bar_Charts.R")) # Requires "PARK_lat_long_Final_Environment.RData". Outputs plots and Excel Workbook 

source(here::here("scripts","Daily_WB_Model.R"))

source(here::here("scripts", "Drought_characteristics.R"))

# source(here::here("scripts", "WBgrid_plotting.R")) # Run the Water Balance Model

source(here::here("scripts", "Return_Events.R"))

source(here::here("scripts", "Summary plots.R"))

source(here::here("scripts", "Report_plots.R"))

```

```{r Copy-and-delete-files, message=FALSE, warning=FALSE, include = FALSE}

source(here::here("scripts", "write_metadata.R"))

source(here::here("scripts", "copy_paste_delete_files.R")) # copies files and folders to specified local folder


```
